### 2020-05-27 system-model.tex
:construction: Phase shift optimization

		For simplicity, we define $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and $\boldsymbol{H}_k=\boldsymbol{h}_k\boldsymbol{h}_k^H$ as waveform matrices and channel matrix of user $k$. Let $\boldsymbol{W}_{I/P,n}$, $\boldsymbol{H}_{k,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{W}_{I/P}$, $\boldsymbol{H}_k$ and null the remaining entries, respectively. Denote $\beta_2={k_2}{R_{\text{ant}}}$ and $\beta_4={k_4}{R_{\text{ant}}^2}$.	On top of this, nonzero terms in \ref{eq:z_k} are detailed in \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end} such that the current expression reduces to \ref{eq:z_k_expand} -- \ref{eq:z_k_waveform}.

@@

\begin{section}{Problem Formulation}
	In this section, we first define the weighted sum rate-energy (WSR-E) region then formulate waveform and IRS optimization problems.
	\begin{subsection}{Weighted Sum Rate-Energy Region}
		Define the achievable WSR-E region as
		\begin{equation}
			\begin{split}
				C_{R-I}(P)
				&\triangleq \biggl\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K u_{P,k}z_k,\\
				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}) \le P\biggr\}
			\end{split}
		\end{equation}
		where $P$ is the transmit power budget and $u_{I,k},u_{P,k}$ are the information and power weight of user $k$.
	\end{subsection}

	\begin{subsection}{Single-User Optimization}
		Consider a single-user waveform and IRS optimization problem where $\boldsymbol{\alpha}=\boldsymbol{1}^{N \times 1}$. We characterize the rate-energy region through a current maximization problem subject to transmit power, rate, and IRS constraints
		\begin{maxi!}
			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
		\end{maxi!}
		Problem \ref{op:su} is intricate due to the non-convex objective function with coupled variables. In the next section, we propose two waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS respectively.

		\begin{subsubsection}{Frequency-Selective IRS}

@@

		\begin{subsubsection}{Frequency-Flat IRS}
			In contrast, frequency-flat IRS reflects all subbands equally with a DoF of $L$. We observe that
			\begin{equation}
				\begin{split}
					\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2
					&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}\\
					&=\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}_n\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})
				\end{split}
			\end{equation}
			where $t$ is an auxiliary variable with unit modulus and
			\begin{equation}
				\boldsymbol{R}_n=
				\begin{bmatrix}
					\boldsymbol{\Phi}_n\boldsymbol{\Phi}_n^H & \boldsymbol{\Phi}_n{h_{D,n}} \\
					h_{D,n}^*{\boldsymbol{\Phi}_n^H}         & h_{D,n}^*{h_{D,n}}
				\end{bmatrix},
				\quad \bar{\boldsymbol{v}}=\
				\begin{bmatrix}
					\boldsymbol{v} \\
					t
				\end{bmatrix},
				\quad \bar{\boldsymbol{V}}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H
			\end{equation}
			Hence, \ref{op:1} is transformed to
			\begin{maxi}
				{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{V},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
				\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
				\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{V},\rho)\ge{\bar{z}}}
				\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
				\addConstraint{\boldsymbol{V}\succeq{0}}
				\addConstraint{\mathrm{rank}(\boldsymbol{V})=1}
			\end{maxi}
			To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the phase shifts and the waveforms with the other being fixed.

			% ? AO: optimize phase shifts with given waveform
			The phase optimization subproblem is formed as follows. For a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, problem \ref{op:temp3} reduces to
			\begin{maxi}
				{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp4}}{}
				\addConstraint{z(\boldsymbol{V})\ge{\bar{z}}}
				\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
				\addConstraint{\boldsymbol{V}\succeq{0}}
				\addConstraint{\mathrm{rank}(\boldsymbol{V})=1}
			\end{maxi}
			To tackle the non-convex current constraint, we collect the channel matrices into $\boldsymbol{\Phi}^H=[\boldsymbol{\Phi}_1,\dots,\boldsymbol{\Phi}_N]^H \in \mathbb{C}^{N \times L}$ and $\boldsymbol{h}=\boldsymbol{h}_D+\boldsymbol{\Phi}^H\boldsymbol{v} \in \mathbb{C}^{N \times 1}$. The fixed waveform matrices are defined as $\boldsymbol{M}_{I/P}=\boldsymbol{w}_{I/P}^*\boldsymbol{w}_{I/P}^T$. On top of this, let $\boldsymbol{M}_{I/P, n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}_{I/P}$ and null the remaining entries. Due to the positive definiteness of $\boldsymbol{M}_{I/P}$, we have $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$. Hence, the output current expression \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_irs}.
			\begin{figure*}[b]
				\hrule
				\begin{equation}\label{eq:z_k_irs}
					\begin{split}
						z
						&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h}+\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})\\
						% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
						% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
						&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})^*+(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})^*}\\
						&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})}
					\end{split}
				\end{equation}
			\end{figure*}
			We further simplify it by introducing auxiliary variables
			\begin{equation}\label{eq:t}
				\begin{split}
					t_{I/P,n}
					&=\boldsymbol{h}^H\boldsymbol{M}_{I/P,n}\boldsymbol{h}\\
					&=\mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{M}_{I/P,n})\\
					&=\mathrm{Tr}(\boldsymbol{R}^H\boldsymbol{V}\boldsymbol{R}\boldsymbol{M}_{I/P,n})\\
					&=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{M}_{I/P,n}\boldsymbol{R}^H\boldsymbol{V})\\
					&=\mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{V})
				\end{split}
			\end{equation}
			where $\boldsymbol{R}^H=[\boldsymbol{\Phi}^H,\boldsymbol{h}_D] \in \mathbb{C}^{N \times (L+1)}$ and $\boldsymbol{C}_{I/P,n}=\boldsymbol{R}\boldsymbol{M}_{I/P,n}\boldsymbol{R}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_irs} rewrites as
			\begin{equation}\label{eq:z_k_irs_t}
				\begin{split}
					z
					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t_{I,0}+t_{P,0})\\
					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2t_{I,n}t_{I,n}^*+t_{P,n}t_{P,n}^*}\\
					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t_{I,0}t_{P,0}
				\end{split}
			\end{equation}

			% It holds that $t_{I/P,n}^*t_{I/P,n}=t_{I/P,-n}^*t_{I/P,-n}$ since $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$. On top of this, denote $\boldsymbol{t}_{I/P}=[t_{I/P,1},\dots,t_{I/P,N-1}]^T \in \mathbb{C}^{(N-1) \times 1}$ and rewrite \ref{eq:z_k_irs} as
			% \begin{equation}\label{eq:z_k_irs_t}
			% 	\begin{split}
			% 		z
			% 		&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t_{I,0}+t_{P,0})\\
			% 		&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}(2t_{I,0}^*t_{I,0}+t_{P,0}^*t_{P,0}+4\boldsymbol{t}_I^H\boldsymbol{t}_I+2\boldsymbol{t}_P^H\boldsymbol{t}_P)\\
			% 		&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t_{I,0}t_{P,0}
			% 	\end{split}
			% \end{equation}
			We use first-order Taylor expansion to approximate the second-order terms in \ref{eq:z_k_irs_t}. Based on the variables optimized at iteration $k - 1$, the local approximations at iteration $k$ are \cite{Adali2010}

@@

					t_{I/P,n}^{(k)} (t_{I/P,n}^{(k)})^*
					& \approx 2 \Re\left\{t_{I/P,n}^{(k)} (t_{I/P,n}^{(k-1)})^*\right\} - t_{I/P,n}^{(k-1)} (t_{I/P,n}^{(k-1)})^* \\
					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{(k-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{V}^{(k)}\right)\right\} - t_{I/P,n}^{(k-1)} (t_{I/P,n}^{(k-1)})^*\\
					& = \mathrm{Tr}\left((t_{I/P,n}^{(k-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{V}^{(k)}\right) + \mathrm{Tr}(t_{I/P,n}^{(k-1)}\boldsymbol{C}_{I/P,n}^H\boldsymbol{V}^{(k)})\\
					& \quad- t_{I/P,n}^{(k-1)} (t_{I/P,n}^{(k-1)})^*

@@

					t_{I,0}^{(k)} t_{P,0}^{(k)}
					& \approx t_{I,0}^{(k)} t_{P,0}^{(k-1)} + t_{I,0}^{(k-1)} t_{P,0}^{(k)} - t_{I,0}^{(k-1)} t_{P,0}^{(k-1)}\\
					& = \mathrm{Tr}(t_{P,0}^{(k-1)}\boldsymbol{C}_{I,0}\boldsymbol{V}^{(k)}) + \mathrm{Tr}(t_{I,0}^{(k-1)}\boldsymbol{C}_{P,0}\boldsymbol{V}^{(k)}) - t_{I,0}^{(k-1)} t_{P,0}^{(k-1)}

@@

			The second approximation holds since $t_{I/P,0}$ are real. Therefore, we have

@@

					\tilde{z}(\boldsymbol{V}^{(k)})
					& = \mathrm{Tr}(\boldsymbol{A}^{(k)}\boldsymbol{V}^{(k)}) \\
					& - \frac{3 k_4 \rho^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2t_{I,n}^{(k-1)} (t_{I,n}^{(k-1)})^* + t_{P,n}^{(k-1)} (t_{P,n}^{(k-1)})^* \\
					& - \frac{3{k_4}{\rho^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{(k-1)} t_{P,0}^{(k-1)}

@@

			where the Hermitian matrix $\boldsymbol{A}^{(k)}$ is
			\begin{equation}\label{eq:A_k}

@@

					\boldsymbol{A}^{(k)}
					& = \frac{k_2 \rho R_{\text{ant}}}{2}(\boldsymbol{C}_{I,0}+\boldsymbol{C}_{P,0})\\
					& \quad+ \frac{3 k_4 \rho^2 R_{\text{ant}}^2}{8}\sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{(k-1)})^*\boldsymbol{C}_{I,n} + t_{I,n}^{(k-1)}\boldsymbol{C}_{I,n}^H\right)\\
					& \quad \quad + \left((t_{P,n}^{(k-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(k-1)}\boldsymbol{C}_{P,n}^H\right)\\
					& \quad+ \frac{3{k_4}{\rho^2}{R_{\text{ant}}^2}}{2} (t_{P,0}^{(k-1)}\boldsymbol{C}_{I,0} + t_{I,0}^{(k-1)}\boldsymbol{C}_{P,0})

@@

			Plug \ref{eq:z_irs_approx} into problem \ref{op:temp4} and solve it by iterative interior-point method. Denote the optimal IRS matrix as $\boldsymbol{V}^{\star}$. If $\mathrm{rank}(\boldsymbol{V}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{v}}^\star$ is attained by eigenvalue decomposition (EVD). Otherwise, a best feasible candidate $\bar{\boldsymbol{v}}^\star$ can be extracted through Gaussian randomization method \cite{Huang2010}. First, we perform EVD on $\boldsymbol{V}^{\star}$ as $\boldsymbol{V}^{\star}=\boldsymbol{U}_{\boldsymbol{V}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{V}^{\star}}\boldsymbol{U}_{\boldsymbol{V}^{\star}}^H$. Then, we generate $R$ random CSCG vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ r=1,\dots,R$ and construct the corresponding candidates $\bar{\boldsymbol{v}}_r=\boldsymbol{U}_{\boldsymbol{V}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{V}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r$. Next, the optimal solution $\bar{\boldsymbol{v}}^\star$ is approximated by the one achieving maximum objective value of \ref{op:temp4}. Finally, we can retrieve the phase shift as $\theta_l=\arg(v_l^\star/v_{L+1}^\star)$. The algorithm for the phase optimization subproblem is summarized in Algorithm \ref{alg:irs}.

>>>>

		For simplicity, we define $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and $\boldsymbol{H}_k=\boldsymbol{h}_k\boldsymbol{h}_k^H$ as waveform matrices and channel matrix of user $k$. Let $\boldsymbol{W}_{I/P,n}$, $\boldsymbol{H}_{k,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{W}_{I/P}$, $\boldsymbol{H}_k$ and null the remaining entries, respectively. Due to the positive definiteness of $\boldsymbol{W}_{I/P}$ and $\boldsymbol{H}_k$, we have $\boldsymbol{W}_{I/P,-n}=\boldsymbol{W}_{I/P,n}^H$ and $\boldsymbol{H}_{k,-n}=\boldsymbol{H}_{k,n}^H$. Let $\beta_2={k_2}{R_{\text{ant}}}$ and $\beta_4={k_4}{R_{\text{ant}}^2}$. On top of this, nonzero terms in \ref{eq:z_k} are detailed in \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end} such that the current expression reduces to \ref{eq:z_k_expand} -- \ref{eq:z_k_waveform}.

@@

	\begin{subsection}{Weighted Sum Rate-Energy Region}
		Define the achievable weighted sum rate-energy (WSR-E) region as
		\begin{equation}
			\begin{split}
				C_{R-I}(P)
				&\triangleq \biggl\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K u_{P,k}z_k,\\
				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}) \le P\biggr\}
			\end{split}
		\end{equation}
		where $P$ is the transmit power budget and $u_{I,k},u_{P,k}$ are the information and power weight of user $k$.
	\end{subsection}
\end{section}

\begin{section}{Single-User Optimization}
	Consider a single-user waveform and IRS optimization problem where $\boldsymbol{\alpha}=\boldsymbol{1}^{N \times 1}$. We characterize the rate-energy region through a current maximization problem subject to transmit power, rate, and IRS constraints
	\begin{maxi!}
			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
		\end{maxi!}
	Problem \ref{op:su} is intricate due to the non-convex objective function with coupled variables. In the next section, we propose two waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS, respectively.

	\begin{subsection}{Frequency-Selective IRS}

@@

	\begin{subsection}{Frequency-Flat IRS}
		In contrast, frequency-flat IRS reflects all subbands equally with a DoF of $L$. We observe that
		\begin{equation}
			\begin{split}
				\lvert{h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}}\rvert^2
				&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{v}_n^H\boldsymbol{\phi}+\boldsymbol{\phi}^H\boldsymbol{v}_n{h_{D,n}}+\boldsymbol{\phi}^H\boldsymbol{v}\boldsymbol{v}^H\boldsymbol{\phi}\\
				&=\bar{\boldsymbol{\phi}}^H\boldsymbol{R}_n\bar{\boldsymbol{\phi}}=\mathrm{Tr}(\boldsymbol{R}_n\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H)=\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})
			\end{split}
		\end{equation}
		where $t$ is an auxiliary variable with unit modulus and
		\begin{equation}
			\boldsymbol{R}_n=
			\begin{bmatrix}
				\boldsymbol{v}_n\boldsymbol{v}_n^H & \boldsymbol{v}_n{h_{D,n}} \\
				h_{D,n}^*{\boldsymbol{v}_n^H}      & h_{D,n}^*{h_{D,n}}
			\end{bmatrix},
			\quad \bar{\boldsymbol{\phi}}=\
			\begin{bmatrix}
				\boldsymbol{\phi} \\
				t
			\end{bmatrix},
			\quad \boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H
		\end{equation}
		with $\boldsymbol{R}_n,\boldsymbol{\Phi} \in \mathbb{C}^{(L+1) \times (L+1)}$ and $\bar{\boldsymbol{\phi}} \in \mathbb{C}^{(L+1) \times 1}$. On top of this, the outer product of composite channel rewrites as
		\begin{equation}
			\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{R}^H\boldsymbol{\Phi}\boldsymbol{R}
		\end{equation}
		where $\boldsymbol{R}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H \in \mathbb{C}^{(L+1) \times N}$. Hence, the output current \ref{eq:z_k_channel} can be reformulated as $z(\boldsymbol{\Phi})$ (details given in section \ref{se:fs_irs}). To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the phase shifts and the waveforms with the other being fixed.

		\begin{subsubsection}{Phase shift optimization}\label{se:fs_irs}
			The phase optimization subproblem is formed as follows. With a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, problem \ref{op:su} reduces to
				{\boldsymbol{\boldsymbol{\Phi}}}{z(\boldsymbol{\Phi})}{\label{op:su_irs}}{\label{eq:su_irs_target}}
				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
				\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}
			\begin{equation}\label{eq:t}
					t_{I/P,n}
					&=\boldsymbol{h}^H\boldsymbol{W}_{I/P,n}^*\boldsymbol{h}\\
					&=\mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,n}^*)\\
					&=\mathrm{Tr}(\boldsymbol{R}^H\boldsymbol{\Phi}\boldsymbol{R}\boldsymbol{W}_{I/P,n}^*)\\
					&=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{W}_{I/P,n}^*\boldsymbol{R}^H\boldsymbol{\Phi})\\
					&=\mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi})
			where we define $\boldsymbol{C}_{I/P,n}=\boldsymbol{R}\boldsymbol{W}_{I/P,n}^*\boldsymbol{R}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_channel} rewrites as
			\begin{equation}\label{eq:z_irs}
					z(\boldsymbol{\Phi})
					&=\frac{1}{2}{\beta_2}{\rho}(t_{I,0}+t_{P,0})\\
					&\quad+\frac{3}{8}{\beta_4}{\rho^2}\sum_{n=-N+1}^{N-1}{2t_{I,n}t_{I,n}^*+t_{P,n}t_{P,n}^*}\\
					&\quad+\frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}
			We use first-order Taylor expansion to approximate the second-order terms in \ref{eq:z_irs}. Based on the variables optimized at iteration $i - 1$, the local approximation at iteration $i$ suggests \cite{Adali2010}

@@

					t_{I/P,n}^{(i)} (t_{I/P,n}^{(i)})^*
					& \approx 2 \Re\left\{t_{I/P,n}^{(i)} (t_{I/P,n}^{(i-1)})^*\right\} - t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^* \\
					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{(i-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi}^{(i)}\right)\right\}\\
					& \quad - t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^*\\
					& = \mathrm{Tr}\left((t_{I/P,n}^{(i-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi}^{(i)}\right)\\
					& \quad + \mathrm{Tr}(t_{I/P,n}^{(i-1)}\boldsymbol{C}_{I/P,n}^H\boldsymbol{\Phi}^{(i)})\\
					& \quad- t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^*

@@

					t_{I,0}^{(i)} t_{P,0}^{(i)}
					& \approx t_{I,0}^{(i)} t_{P,0}^{(i-1)} + t_{I,0}^{(i-1)} t_{P,0}^{(i)} - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\\
					& = \mathrm{Tr}(t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) + \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0}\boldsymbol{\Phi}^{(i)})\\
					& \quad - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}

@@

			Therefore, the approximated current function at iteration $i$ is

@@

					\tilde{z}(\boldsymbol{\Phi}^{(i)})
					& = \mathrm{Tr}(\boldsymbol{A}^{(i)}\boldsymbol{\Phi}^{(i)}) \\
					& - \frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{(i-1)} (t_{I,n}^{(i-1)})^* + t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^* \\
					& - \frac{3}{2} \beta_4 \rho^2 t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}

@@

			where the corresponding Hermitian matrix $\boldsymbol{A}^{(i)}$ is
			\begin{equation}\label{eq:A}

@@

					\boldsymbol{A}^{(i)}
					& = \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{I,0}+\boldsymbol{C}_{P,0})\\
					& \quad+ \frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{(i-1)})^*\boldsymbol{C}_{I,n} + t_{I,n}^{(i-1)}\boldsymbol{C}_{I,n}^H\right)\\
					& \quad \quad + \left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H\right)\\
					& \quad+ \frac{3}{2} \beta_4 \rho^2 (t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0} + t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0})

@@

			We then plug \ref{eq:z_irs_approx} into problem \ref{op:su_irs}, relax the rank constraint \ref{co:irs_rank}, and obtain the optimal IRS matrix $\boldsymbol{\Phi}^{\star}$ by interior-point method. If $\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is attained by eigenvalue decomposition (EVD). Otherwise, a best feasible candidate $\bar{\boldsymbol{\phi}}^\star$ can be extracted through Gaussian randomization method \cite{Huang2010}. First, perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$. Then, generate $R$ CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ r=1,\dots,R$ and construct the corresponding candidates $\bar{\boldsymbol{\phi}}_r=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r$. Next, the optimal solution $\bar{\boldsymbol{\phi}}^\star$ is approximated by the one achieving maximum objective value \ref{eq:su_irs_target}. Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star)$. The algorithm for the phase optimization subproblem is summarized in Algorithm \ref{al:ff_irs}.
				\caption{FF-IRS: Phase Shift Optimization}
				\label{al:ff_irs}
					\State \textbf{Input} $\bar{R},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$
					\State \textbf{Initialize} $i \leftarrow 0,\boldsymbol{\Phi}^{(0)},\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}
					\State Update SDR matrix $\boldsymbol{A}^{(i)}$ by \ref{eq:A}
					\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs}
					\State Update auxiliary $t_{I/P,n}^{(i)} \forall n$ by \ref{eq:t} for SCA
					\Until $\lvert R^{(i)}-R^{(i-1)} \rvert \le \epsilon$
					\State Perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$
					\State Generate CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall r$
					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_r=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r$ and corresponding matrices $\boldsymbol{\Phi}_r=\bar{\boldsymbol{\phi}}_r\bar{\boldsymbol{\phi}}_r^H  \ \forall r$
					\State Select the best solution $\boldsymbol{\Phi}^\star$ for problem \ref{op:su_irs} and corresponding $\boldsymbol{\phi}^\star$
					\State Compute IRS phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
					\State \textbf{Output} $\theta_l, \ l=1,\dots,L$

		\begin{subsubsection}{Waveform optimization}
			The waveform optimization subproblem is formed as follows. Once $\boldsymbol{\Phi}$ is obtained, problem \ref{op:su} is reduced to
